# Signatories
<!-- 
This section provides the ISC with a view of the support received from the community for a proposal. Acceptance isn't predicated on popularity but community acceptance is important.  Willingness to accept outside input is also a good marker for project delivery. 

An optional section would be for R-Core signatories where changes to R are proposed.
-->

## Project team

### Steph Locke
Steph's a Principal Consultant at Mango Solutions and runs user groups & conferences in her spare time. She runs R, SQL, and .Net user groups in Cardiff, UK, and organises national conferences called SQL Relay. Over the past 3 years she's organised 25 days of SQL Relay conferences in more than 12 locations. Most recently, Microsoft made her a Data Platform Most Valued Professional for her community work in and around SQL Server and R.

### Gergely Daroczi

## Interested parties

```{r load_data, echo = FALSE}
## load anonymized data from the referenced Google Spreadsheet
## NOTE this is a manual "copy and paste" (!) of the survey responses
##      into a new spreadsheet, as there is no other way to clear
##      the e-mail addresses from the revision history
library(googlesheets)
responses <- gs_key('1bkHGoae_j3Ikp3Bw7AO9kxCu_tC2HSzGhvlSMskGHvI', visibility = 'public', verbose = FALSE)
responses <- gs_read(responses, ws = 1, range = cell_rows(1:322), verbose = FALSE)

## data.table showcase
library(data.table)
responses <- data.table(responses)

## programmer-friendly column names
setnames(responses, c('region', 'location', 'travel', 'roles'))
```

We've had tremendous support from the community over the length of developing the proposal. From the first comments on the [initial blog post](http://itsalocke.com/sqlsaturdays-but-for-r/), to active discussion on the [repository](https://github.com/stephlocke/RSaturday-proposal), to `r responses[, .N]` people signing up as interested parties towards the end of the proposal development cycle. Below is a breakdown of the interested parties per region:

```{r plot_region, echo = FALSE, fig.width = 10, fig.height = 5, results = 'hide'}
## order factor levels based on the number of respondents
responses[, region := factor(region, levels = responses[, .N, by = region][order(N), region])]

## plotnumber of interested parties per region
suppressPackageStartupMessages(library(ggplot2))
ggplot(responses, aes(x = region)) +
  geom_bar(fill = '#2165B6') + theme_bw() + coord_flip() +
  geom_text(data=responses[,.N,region],aes(y = N , label = N),
            color = 'white', hjust = 1.3) +
  xlab('') + ylab('') + ggtitle('What part of the world are you in?')
```

<!--
A more detailed breakdown of the location of the interested parties:

```{r plot_map, echo = FALSE, fig.width = 10, fig.height = 7}
## geocode locations
suppressPackageStartupMessages(library(ggmap))
responses[, c('lon', 'lat') := geocode(location, )]

## map points on a world-map with the weight of interested parties at the same location
library(maps)
ggplot(map_data('world')) +
  geom_polygon(aes(x = long, y = lat, group = group), fill = 'grey90', colour = 'white') + 
geom_point(aes(x = lon, y = lat, size = N), color = '#2165B6',
           data = responses[, .N, by = .(lon, lat)]) +
  xlab('') + ylab('') + ggtitle('Where do you live?') +
  theme_minimal() + theme('legend.position' = 'top')

```
-->
We also asked how far the interested parties are willing to travel for an satRday event:

```{r plot_travel, echo = FALSE, fig.width = 10, fig.height = 5, results = 'hide'}
## fix factor levels
responses[, travel := factor(travel, levels = rev(c(
                                         'To my nearest city',
                                         'To anywhere in my country',
                                         'To anywhere in my continent',
                                         'To anywhere in the the world')))]

## plot the number of interested parties willing to travel
ggplot(na.omit(responses), aes(x = travel)) +
  geom_bar(fill = '#2165B6') + theme_bw() + coord_flip() +
  geom_text(data=responses[,.N,travel],aes(y = N , label = N),
            color = 'white', hjust = 1.3) +
  xlab('') + ylab('') + ggtitle('How far are you willing to travel?')
```

It seems that most respondents are interested in local events, but quote many (~`r round(responses[travel != 'To my nearest city', .N] / responses[, .N] * 100)`%) respondents are willing to travel as well.

Further great news and promising feedback from the community is that the respondents are willing to actively take part in future events:

```{r plot_activity, echo = FALSE, fig.width = 10, fig.height = 5}
## split list of promises
promises <- unlist(strsplit(responses[, roles], ', '))

## remove "other" answers
promises <- promises[promises %in% c('Attending a satRday',
                                     'Helping out a satRday',
                                     'Helping publicise the events',
                                     'Presenting at a satRday',
                                     'Organising a satRday',
                                     'Helping improve the website',
                                     'Helping with central organisation',
                                     'Sponsoring an event')]

## order factor levels based on the number of respondents
promises <- factor(promises, levels = names(sort(table(promises))))

## plot the number of interested parties willing to do stuff
ggplot(data.table(promises), aes(x = promises)) +
  geom_bar(fill = '#2165B6') + theme_bw() + coord_flip() +
  geom_text(data=data.table(promises)[,.N,promises],aes(y = N , label = N),
            color = 'white', hjust = 1.3) +
  xlab('') + ylab('') + ggtitle('What role(s) are you interested in?')
```

We already have more than `r floor(sum(promises == 'Presenting at a satRday') / 100) * 100` presenters, almost `r ceiling(sum(promises == 'Attending a satRday') / 100) * 100` attendees and `r sum(promises == 'Helping improve the website')` webmasters -- what can go wrong?
